Consistent Polyhedral Surrogates via Embedding

### 2019-05-16 neurips-19/poly-embed.tex
titles...
Made another pass over proof sketches

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification or ranking. 
In this approach, one embeds each of the finitely many predictions (e.g. classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in between to obtain a surrogate.  
We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.  
Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.  
We illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
\end{abstract}

>>>>

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification or ranking. In this approach, one embeds each of the finitely many predictions (e.g. classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in between to obtain a surrogate.  
We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.  
Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.  
We go on to illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
\end{abstract}
\end{document}

### 2019-05-16 notes/jessie-proof-sketches.tex
Made another pass over proof sketches

  For the reverse implication, see proof below.
  \jessie{I don't see a way that properties make this easier.}

\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
  \jessie{Incomplete...?}
\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}[Property version]
  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral.

  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$, \jessie{for appropriate choice of $\R$} elicited by the discrete loss $\ell$. 
  Thus, $L$ embeds $\ell$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
  Therefore, $\risk{L}$ is polyhedral.

@@

  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
\end{proof}
\hrulefill
\begin{proof}[Property version]
  To see this, we construct one such discrete loss, namely $L|_\R$, where $\R := \{u_f\}_{f \in F}$ is the set of reports that are uniquely optimal on the interior of each full-dimensional level set.

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}[Property version]
  Consider $\gamma := \prop{\ell}$.
  The result is a corollary of Theorem~\ref{thm:general-duality-embedding}, where $L$ is as constructed in the proof.
\end{proof}
\hrulefill
\begin{proof}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  \jessie{Might try tonight without properties?}
\end{proof}

>>>>

  For the reverse implication, see proof below.
  \jessie{I don't see a way that COLT results make this easier, since we don't talk about Bayes Risk that much.}
  Consider 
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.

  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\cite[Theorem 2]{frongillo2014general} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$, which is a sufficient condition for embedding.
\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}[Property version]
  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
  \jessie{This direction is shorter below without properties.}

  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
  For the set of facets $F$ of the surface of $\risk{L}$, construct $\R := \{u_f\}_{f \in F}$. 
  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $\ell := L|_\R$. 
  Thus, $L$ embeds $\ell$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
  Therefore, $\risk{L}$ is polyhedral.

@@

  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
\end{proof}
\hrulefill
\begin{proof}[Property version]
  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
  As before, construct, $\R = \{u_f\}_{f \in F}$ for the uniquely optimal report associated with the interior of each facet of the loss surface on $\risk{L}$.
  To see our result, we specifically show that $L$ embeds $L|_\R$.

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}[Property version]
  Consider $\gamma := \prop{\ell}$.
  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where $L$ is as constructed in the proof.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
  Now construct $L$ as in \cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$.
  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
\end{proof}
